### 2023-02-20 README.Rmd
Update README.Rmd

# minTEMU - The Legacy of the European Postgraduate Master in Urbanism at TU Delft: A Text Mining Approach

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/UD3-Lab/minTEMU/master?urlpath=rstudio)

>>>>

# mintEMU - The Legacy of the European Postgraduate Master in Urbanism at TU Delft: A Text Mining Approach

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/UD3-Lab/minTEMU/main?urlpath=rstudio)
